\newpage
\chapter*{Список литературы:}
\addcontentsline{toc}{chapter}{Список
  Литературы}
\begin{enumerate}
\item \textit{Nielsen M.A., Chuang I.L.} Quantum Computation and Quantum
Information // Cambrige: Cambrige University Press -- 2000.\label{lit:nil-chang}
\item \textit{Валиев К.А., Кокин А.А.} Квантовые компьютеры: надежды и
  реальность // 2-е изд. М. -- Ижевск: НИЦ РХД -- 2002. -- 360
  с. \label{lit:valiev-kokin}
\item \textit{Валиев К.А.} Квантовые компьютеры и квантовые вычисления //
  УФН -- 2005. -- Т. 175. -- С. 3-39.\label{lit:valiev}
\item \textit{G.D. Fuchs, V.V. Dobrovitski, D.M. Toyli, F.J. Heremans,
  D.D. Awschalom} Gigahertz Dynamics of a Strongly Driven Single
  Quantum Spin // Science 11 December -- 2009. -- V. 326. -- no. 5959
  pp. 1520-1522 DOI: 10.1126/science.1181193\label{lit:gigahertz}
\item \textit{Chuang I.L., Gershenfeld N., Kubinec M.G., Leung D.W.} Bulk
  quantum computation with nuclear magnetic resonance: theory and
  experiment //
  Proc. Roy. Soc. Lond -- 1998. -- V. A454. -- P.\label{lit:first-demonstration}
\item \textit{Robledo L., Bernien H., van Weperen I., Hanson R.} Control and
  coherence of the optical transition of single nitrogen vacancy
  venters in diamond //
  Phys. Rev. Lett -- 2010. -- V. 105. -- P. 177403.\label{lit:excitef-oscilations}
\item \textit{Collins, A.T., Thomaz, M.F., Jorge, M. I. B.}
  Luminescence decay time of the 1.945 eV centre in type Ib diamond //
  Journal of Physics -- 1983. -- C 16 (11): 2177.\label{lit:lumin-collins}
\item \textit{Hanzawa, H., Nisida, Y., Kato, T.} Measurement of decay
  time for the NV centre in Ib diamond with a picosecond laser pulse
  // Diamond and Related Materials -- 1997. -- 6 (11): 1595.\label{lit:lumin-Hanzawa}
\item \textit{Shi F., Rong X., Xu N., Wang Y., Wu J., Chong B., Peng X.,
  Kniepert J., Schoenfeld R.S., Harneit W., Feng M., Du
  J.} Room-temperature implementation of the Deutsch-Jozsa algorithm
  with a single electronic spin in diamond //
  Phys. Rev. Lett -- 2010. -- V. 105. -- P. 040504.\label{lit:nv-deutsch}
\item \textit{Цуканов А.В.} Сверхпроводящие резонаторы и зарядовые
  кубиты: спектроскопия и квантовые операции. Часть I //
  Микроэлектроника -- 2010. -- Т. 39. -- C. 404.\label{lit:tsukanov-super-cond-one}
\item \textit{Цуканов А.В.} Сверхпроводящие резонаторы и зарядовые кубиты:
  спектроскопия и квантовые операции. Часть II //
  Микроэлектроника -- 2011. -- Т. 40. -- C. 11.\label{lit:tsukanov-super-cond-two}
\item \textit{Yamamoto Y., Ladd T.D., Press D.,  Clark S., Sanaka K., Santori
  C., Fattal D., Fu K.M., Höfling S., Reitzenstein S., Forchel
  A.} Optically controlled semiconductor spin qubits for quantum
  information processing //
  Phys. Scripta -- 2009. -- V. T139. -- P. 014010.\label{lit:dots}
\item \textit{Kane B.E.} A silicon-based nuclear spin quantum computer //
  Nature -- 1998. -- V. 393. -- P. 133.\label{lit:implant}
\item \textit{Monz, Thomas} 14-Qubit Entanglement: Creation
  and Coherence // Physical Review Letters (American Physical
  Society) -- 2011. -- March 31\label{lit:ion-trap}
\end{enumerate}

